Using statistics to guide response to the HIV epidemic

### 2023-05-18 src/docs_17-05-23-hi-med/17-05-23-hi-med.Rmd
Correct typo #144

```{r echo=FALSE, out.width="350px", fig.cap = "A total of 46 surveys: importantance of good data processing code!"}
knitr::include_graphics("depends/available-surveys.png")
```

>>>>

```{r echo=FALSE, out.width="350px", fig.cap = "A total of 46 surveys: importance of good data processing code!"}
knitr::include_graphics("depends/available-surveys.png")
```
